
\documentclass[11pt]{article}
\usepackage{texab}
\usepackage{a4}

\def\note#1{\\ *** \emph{#1}\\}
\def\T{\texttt}
\def\code{\texttt}

\begin{document}

\section{Programming notes}
\Itm
regr: handling of data, subset, weights, ...
is subtile: weights may need to be evaluated before subset is taken.\\
The elimination of unused levels might be deferred to model.frame using the
argument \T{drop.unused.levels} -- 
but some fitting functions (at least \T{survreg}) do not pass the argument
on to it.\\
The component \T{\$allvars} of the \T{regr} result is good enough for 
\T{add1}. Therefore, the data argument is copied to the \T{\$funcall}
component of the result.

\Itm % nov 15
Binary factors: have a different name in drop1 than in coef.
\Arrow Use attr(\$x, "assign") and attr(\$terms,"term.labels")

\Itm
Factors created in the formula statement are difficult to handle
by plresx. They get a flag as \T{is.fac==2}, and fitcomp needs to know
that.
(Consider such strange terms as \T{factor(2*stelle), factor(pmin(a,b))})

\Itm
A namespace catch:\\
I export \T{Surv, strata, cluster} which come from the package
\T{survreg}, since otherwise, they cannot be used in formulas
unless \T{survreg} is loaded.

%% =======================================================================
\section{The Function \T{regr}}
\Tit{Arguments to regr}
\Itm
\T{family} % and \T{dist}
\T{normal = gaussian, binomial, poisson, gamma, cumlogit, multinomial,
weibull, lognormal, logistic, loglogistic, extreme, t}\\
\note{add cumloglog, ... for polr}
depends on type of response, which may be
\T{numeric, nmatrix, binary, bincount, ordered, factor}
\note{bincount defined by function Bincount}
\T{survival}: default ``family'' is \T{ph}, but others are available,
\T{"weibull"},...\\
Attribute \T{distribution} of y sets default for \T{family}\\
\T{Tobit} entails \T{family="gaussian"} as a default

\Itm
\T{method} !!! changed
\T{lm, rlm, nls, glm, polr, multinom, survreg, coxph}
\note{coxph needs definition of residuals}

\Tit{Value of regr}
Term table:
Coefficients for terms with a single coefficient.
Zero degrees of freedom in some case of interactions: continuous times
factor (obtained in survreg)

\Tit{eval and match.call}
When a call is generated within a function by modifying \T{match.call()}, 
and this function is evaluated, 
\T{match.call} is evaluated at the parent level and therefore does not 
yield the arguments of the function in which it is called. 
[This cost me about six hours to find out.]

\Tit{Save residuals etc. witout NAs!}
I was tempted several times to expand such results to full length.
But then, the extractor functions would not work as foreseen
(or na.action would have to be set to NULL in the regr result.
This could make it incompatible with other functions provided by plain R).

Nevertheless, \T{largs\$pldata} and \T{simresiduals} are full size.
And plotting functions use full size.
%% =================================================================
\section{Contrasts}
contr.wsum

contr.wpoly: orthogonalize wrt the design, not the scores.
$-> X^TX=$diag = $S^T W S$, if the rows of $S$ correspond to the scores.

Binary variables, whether 0-1, logical, or 2 level factors,
should get treatment contrasts by default for easy interpretation 
of the coefficient as well as coefficients of interactions.
But may also be centered (wrt the data.frame, not at 0.5);
which should be obtained either from contr.wpoly or by a tiny separate
function that does the same (to be done...).

%% =================================================================
\section{drop1, add1, step}
\Tit{NAs and subset}
NAs 
\Itm in resppmse \Arrow shorter object\$residual
\Itm in starting model \Arrow same
\Itm in add1 scope 

\Tit{step}
is modified. Why???

\Tit{drop1 and survreg}
\T{object\$df} is \T{length(coef)+1} instead of
\T{length(coef)-intercept}
%% =================================================================
\section{Residuals}
\Tit{Component Effects}
with interactions ?

\Tit{Fuzzy Residuals}
conditional distribution

%% =================================================================
\section{Residual Plots}
\Tit{QQ-plots}
not for glm. adequate distribution! (make sure for Gamma, weibull, ...!)

Conditional: show segments ony if conditional probability in range given by 
\T{condprobrange}

%% =================================================================
\section{Plot.regr, plresx}
\Itm
\T{plotregrControl}:\\
a. handle arguments
\\
b. evaluate data arguments\\
   make all data arguments consistent = full size\\
Collect all variables in \T{formula}

     subset: blow up?

need to store \T{yexpr}, the expression that generates the response,
for use in \T{yfit} section of \T{plot.regr}.

\Tit{Weights for plotting sizes}
plweights / weights:
NULL or NA: use x\$weights if available (glm?)\\
TRUE: same, warning if not available\\
FALSE: do not use them.\\
vector or name: evaluate to use as weights\\
\Arrow need to first evaluate 'weights' in 'data' since it may be a name of it.

cex.plab : size for text labels and points
if negative, the sizes will be  -cex.plab*plweights  (if any weights)

\Tit{getVars} replaces \T{get\_all\_vars} and \T{model.frame}.\\
 different error handling; names of extras with .

pch, plab, pcol can be generated by evaluation in the data.

\Tit{i.getplrdata}
formula  
All 'extras': plab, pch, ... 
  are evaluated in 'data'. 
  Special care for 'plweights = TRUE' or 'FALSE' or NA
value:\\
pldata
  variables
  plab, pch, col, smooth.group, weight  (in ())
    weights as x-variable: not here
residuals
stres
  modified by hatlim --> regr needs it, too, separate fn!
strratio
absres
resmahal
fitted
... names
sigma
wgt
wsymb

\Tit{colors}
simulated smooths: work with color.pale, not only for smooth.group

\Tit{Plot ranges}

\Tit{smooth.group}

\Tit{Residuals from smooth}
check! and document!

\Tit{sequence}
do not include in \T{plotselect}, give as separate argument

\section{Inner and outer range}
Argument \T{ylim} can be a range or a logical.

\Tit{plot.regr and plresx}
only one set of limits can be given in a call.
If different limits would be needed, separate calls are necessary.
I assume that another mechanism (lists) would be too complicated
and never be used.

\Tit{pllimits}
determines inner plotting range.
Data is a vector or a matrix.
Result is either the first argument, unless that is either 
\T{NULL}, \T{NA}, \T{TRUE} or \T{FALSE}. In the latter case,
the first 3 values lead to the determination of the range by using 
\T{robrange}.
Then, the result is a matrix of 2 rows and as many columns as \T{data} has.
If the first argument is \T{FALSE}, the matrix will consist of
elements equal \T{FALSE}.

%% =================================================================
\section{Smooths}
Functions:

%%- \Itm
%%- \code{smoothMM} calls \code{smoothM} calls \code{smooth}, 
%%- which is \code{smoothRegr} by default.\\
%\code{smoothMM}: 
%%- Smooths for multiple x and y, needed for multivariate regression.
%%- Yields a list of lists.\\
%\code{smoothMM} is 
\Itm
\code{smoothM}: smooth for multiple y, generating smooths by group. 
Yields a list.
Called from \code{i.plotlws} or, in the case of
resdiduals from smooth (for qq and TAscale), by \code{plot.regr}.
\Itm
\code{smoothRegr} is essentially \code{loess}, with suitable parameter, 
and provides error handling. 
Returns NULL if less than 8 observations are provided.


\code{smooth.group}: do separate smooths for each group\\
Simulated smooths clutter the plot in this case, therefore, the default
\code{smooth.sim} is then set to 0.

%% =================================================================
\section{Documentation of Output}
tit and doc.

stamp

%% ==================================================================
\section{Miscellaneous}
\Itm
bookkeeping in lm

\$x = model.matrix, includes\\
  colnames= names of coef\\
  attr(,"assign") zuordnung zu term.labels, die aber nicht da sind\\
  attr(,"contrasts") for factors

\Itm
options ... mgp, 

\Itm
draw unimportant, extended items (reference lines, smooths) first



\end{document}



%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
